Blum axioms and nondeterministic computation of functions

### 2016-04-20 paper.tex
paper.tex: Simplify the exposition of time/space complexity example.

\begin{example}
    The standard measures of time and space can be constructed
    over the acceptable numbering of example~\ref{standard-numbering}.
    The time complexity is simply the number of moves the machine makes before halting;
    if it does not halt, leave it undefined.
    As this number is only defined if the machine halts,
    the first axiom is satisfied;
    and, to decide the predicate of the second axiom,
    we can simply run the machine for $k$ moves and see whether it halted.

    Space complexity requires extra care,
    because the machine might not halt
    even though the number of tape cells it uses is limited.
    So, define the corresponding function $\Phi$ by
    \begin{equation*}
        \Phi(w, x) = \begin{cases}
            k, &\text{if $w$ scans exactly $k$ tape cells and halts when processing $x$}\\
            \text{undefined}, &\text{if $w$ never halts on $x$}
        \end{cases}
    \end{equation*}
    This function satisfies the first axiom,
    and, as there is a finite number of states of computation
    in which at most $k$ tape cells are scanned,
    the predicate of the second axiom can be verified
    by keeping all intermediate steps of computation
    and checking to see whether any state repeat
    (in this case, the machine loops and the complexity is undefined).
\end{example}

>>>>

\begin{example}
    The standard measures of time and space can be constructed
    over the acceptable numbering of example~\ref{standard-numbering}.
    They are, respectively,
    the number of moves and tape cells scanned
    before halting.
    Leave the complexity undefined if the machine does not halt
    --- this satisfies the first axiom.
    The predicate of the second axiom is simple for time complexity;
    for space complexity,
    we must keep the whole history of computation
    to make sure the machine does not loop in a limited amount of space
    (because the complexity is not defined in this case).
\end{example}
